Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-06-04 analysis/paper/paper.Rmd
Edits to the methods

Each article was rated on a 0 -- 3 scale for its software, data and code availability.
'Software availability' was defined as follows, a score of '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used.
'Code availability' scores were assigned as '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
Lastly, the 'Data availability' was evaluated as '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.

@@

Efforts were made to standardise the scoring as much as possible.
A custom function, `import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2022].
Values for software packages were checked for spelling consistency and corrections were made manually where necessary.
When working with these data in R, all strings of software character values were converted to fully upper-case to standardise the capitalisation and alleviate any issues with capitalisation used between evaluators.
In some cases the `software_avail`, or the openness of the software used, score did not agree with the software that was recorded and the agreed-upon criteria, so these scores were modified after discussion to match the ratings to the record of the software that was used in each respective paper.
For example, a paper was rated as having a `software_avail` rating of `3`, but the evaluator noted that Excel had been used; here, the `software_avail` rating was changed to `2` to bring it into line with the agreed upon guidelines.
In other cases, papers did not adequately describe all the software used, e.g., GenAlEx, an Excel add-on, was referred to but Excel was not mentioned in the text.
Here, Excel was added to the `software_used` column and the `software_avail` score was adjusted accordingly.
The software availability, computational methods availability and data availability scores were converted from 0 -- 3 to 1 -- 4 ordinal score values for analysis.

>>>>

Each article was rated on a 0 -- 3 scale for its software, data and code availability.
'Software availability' rated how freely and openly available the software used was.
It was defined as follows, a score of '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used.
'Code availability' rated how easily and openly available the computational methods used in the article were.
Scores were assigned as '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable.
Lastly, the 'Data availability' evaluated how freely and openly available the data presented in the article were.
This was evaluated as '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.

@@

A custom function, `import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2022].
Values for software packages were checked for spelling consistency and corrections were made manually where necessary.
When working with these data in R, all strings of software character values were converted to fully upper-case to standardise the capitalisation and alleviate any issues with capitalisation used between evaluators.
In some cases the `software_avail`, or the openness of the software used, score did not agree with the software that was recorded and the agreed-upon criteria, so these scores were modified after discussion to match the ratings to the record of the software that was used in each respective paper.
For example, a paper was rated as having a `software_avail` rating of `3`, but the evaluator noted that Excel had been used; here, the `software_avail` rating was changed to `2` to bring it into line with the agreed upon guidelines.
In other cases, papers did not adequately describe all the software used, e.g., GenAlEx, an Excel add-on, was referred to but Excel was not mentioned in the text.
Here, Excel was added to the `software_used` column and the `software_avail` score was adjusted accordingly.
The software availability, computational methods availability and data availability scores were converted from 0 -- 3 to 1 -- 4 ordinal score values for analysis.
